A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs

### 2015-06-21 paper/paper.tex
Layout
Use rightarrowtail for non-induced subisos

\begin{enumerate}
    \item We introduce supplemental graphs, which generalise some of the ideas in SND. The key idea
        is that a subgraph isomorphism $i : P \hookrightarrow T$ induces a subgraph isomorphism
        $F(i) : F(P) \hookrightarrow F(T)$, for certain functors $F$.  This is used to generate
        implied constraints: we may now look for a mapping which is simultaneously a subgraph
        isomorphism between several carefully selected pairs of graphs.

@@

A \emph{non-induced subgraph isomorphism} is an injective mapping $i : P \hookrightarrow T$ from a
graph $P$ to a graph $T$ which preserves adjacency---that is, if $v \sim_{P} w$ then we require
$i(v) \sim_{T} i(w)$ (and thus if $v$ has a loop, then $i(v)$ must have a loop). The
\emph{non-induced subgraph isomorphism problem} is to find such a mapping from a given pattern graph
$P$ to a given target graph $T$.  (The \emph{induced subgraph isomorphism problem} additionally
requires that if $v \not\sim_{P} w$ then $i(v) \not\sim_{T} i(w)$; we discuss only the non-induced
version in this paper. Both variants are \NP-complete.)

@@

\begin{proposition}\label{proposition:supplemental}
    Let $i : P \hookrightarrow T$ be a subgraph isomorphism. Then $i$ is also
    \begin{enumerate}[itemindent=1em,topsep=2pt,itemsep=0.2pt]
        \item a subgraph isomorphism $i^d : P^d \hookrightarrow T^d$ for any $d \ge 1$, and
        \item a subgraph isomorphism $i^{\left[c, l\right]} : P^{\left[c, l\right]} \hookrightarrow
            T^{\left[c, l\right]}$ for any $c, l \ge 1$.
    \end{enumerate}
\end{proposition}

@@

\begin{algorithm}[h]
\DontPrintSemicolon
\nl $\FuncSty{createSupplementalGraphList}$ (Graph $\mathcal{P}$, Graph $\mathcal{T}$) $\rightarrow$ GraphPairs \;
\nl \Begin{
    \nl $\begin{aligned}\KwSty{return}~\Big[
            &(\mathcal{P},\ \mathcal{T}),
            &&(\mathcal{P}^{\left[1,2\right]},\ \mathcal{T}^{\left[1,2\right]}),
            &&(\mathcal{P}^{\left[2,2\right]},\ \mathcal{T}^{\left[2,2\right]}),
            &&(\mathcal{P}^{\left[3,2\right]},\ \mathcal{T}^{\left[3,2\right]}), \\
            &&&(\mathcal{P}^{\left[1,3\right]},\ \mathcal{T}^{\left[1,3\right]}),
            &&(\mathcal{P}^{\left[2,3\right]},\ \mathcal{T}^{\left[2,3\right]}),
            &&(\mathcal{P}^{\left[3,3\right]},\ \mathcal{T}^{\left[3,3\right]})
    \Big]\end{aligned}$ \;
}
\caption{Supplemental graphs for \cref{algorithm:sip}}
\label{algorithm:supplemental}
\end{algorithm}

\Cref{algorithm:init} is responsible for initialising domains. We have a variable for each vertex in
the (original) pattern graph, with each domain being the vertices in the (original) target graph. It
is easy to see that a vertex of degree $d$ in the pattern graph $P$ may only be mapped to a vertex in
the target graph $T$ of degree $d$ or higher: this allows us to perform some initial filtering. By
extension, we may use compatibility of neighbourhood degree sequences: $v$ may only be mapped to $w$
if $\operatorname{S}(P, v) \preceq \operatorname{S}(T, w)$ \cite{Zampelli:2010}.  Because any
subgraph isomorphism $P \hookrightarrow T$ is also a subgraph isomorphism $F(P) \hookrightarrow
F(T)$ for any of our supplemental graph constructions $F$, we may further restrict initial domains
by considering only the intersection of filtered domains using each supplemental graph pair
individually (\lineref{line:filter}). At this stage, we also enforce the ``loops must be mapped to loops'' constraint.

>>>>

\begin{enumerate}
    \item We introduce supplemental graphs, which generalise some of the ideas in SND. The key idea
        is that a subgraph isomorphism $i : P \rightarrowtail T$ induces a subgraph isomorphism
        $F(i) : F(P) \rightarrowtail F(T)$, for certain functors $F$.  This is used to generate
        implied constraints: we may now look for a mapping which is simultaneously a subgraph
        isomorphism between several carefully selected pairs of graphs.

@@

A \emph{non-induced subgraph isomorphism} is an injective mapping $i : P \rightarrowtail T$ from a
graph $P$ to a graph $T$ which preserves adjacency---that is, if $v \sim_{P} w$ then we require
$i(v) \sim_{T} i(w)$ (and thus if $v$ has a loop, then $i(v)$ must have a loop). The
\emph{non-induced subgraph isomorphism problem} is to find such a mapping from a given pattern graph
$P$ to a given target graph $T$.  (The \emph{induced subgraph isomorphism problem} additionally
requires that if $v \not\sim_{P} w$ then $i(v) \not\sim_{T} i(w)$; we discuss only the non-induced
version in this paper. Both variants are \NP-complete.)

@@

\begin{proposition}\label{proposition:supplemental}
    Let $i : P \rightarrowtail T$ be a subgraph isomorphism. Then $i$ is also
    \begin{enumerate}[itemindent=1em,topsep=2pt,itemsep=0.2pt]
        \item a subgraph isomorphism $i^d : P^d \rightarrowtail T^d$ for any $d \ge 1$, and
        \item a subgraph isomorphism $i^{\left[c, l\right]} : P^{\left[c, l\right]} \rightarrowtail
            T^{\left[c, l\right]}$ for any $c, l \ge 1$.
    \end{enumerate}
\end{proposition}

@@

\begin{algorithm}[t]
\DontPrintSemicolon
\nl $\FuncSty{createSupplementalGraphList}$ (Graph $\mathcal{P}$, Graph $\mathcal{T}$) $\rightarrow$ GraphPairs \;
\nl \Begin{
    \nl $\begin{aligned}\KwSty{return}~\Big[
            &(\mathcal{P},\ \mathcal{T}),
            &&(\mathcal{P}^{\left[1,2\right]},\ \mathcal{T}^{\left[1,2\right]}),
            &&(\mathcal{P}^{\left[2,2\right]},\ \mathcal{T}^{\left[2,2\right]}),
            &&(\mathcal{P}^{\left[3,2\right]},\ \mathcal{T}^{\left[3,2\right]}), \\
            &&&(\mathcal{P}^{\left[1,3\right]},\ \mathcal{T}^{\left[1,3\right]}),
            &&(\mathcal{P}^{\left[2,3\right]},\ \mathcal{T}^{\left[2,3\right]}),
            &&(\mathcal{P}^{\left[3,3\right]},\ \mathcal{T}^{\left[3,3\right]})
    \Big]\end{aligned}$ \;
}
\caption{Supplemental graphs for \cref{algorithm:sip}}
\label{algorithm:supplemental}
\end{algorithm}

\Cref{algorithm:init} is responsible for initialising domains. We have a variable for each vertex in
the (original) pattern graph, with each domain being the vertices in the (original) target graph. It
is easy to see that a vertex of degree $d$ in the pattern graph $P$ may only be mapped to a vertex in
the target graph $T$ of degree $d$ or higher: this allows us to perform some initial filtering. By
extension, we may use compatibility of neighbourhood degree sequences: $v$ may only be mapped to $w$
if $\operatorname{S}(P, v) \preceq \operatorname{S}(T, w)$ \cite{Zampelli:2010}.  Because any
subgraph isomorphism $P \rightarrowtail T$ is also a subgraph isomorphism $F(P) \rightarrowtail
F(T)$ for any of our supplemental graph constructions $F$, we may further restrict initial domains
by considering only the intersection of filtered domains using each supplemental graph pair
individually (\lineref{line:filter}). At this stage, we also enforce the ``loops must be mapped to loops'' constraint.
